\chapter{Legal Notices}

\section{Introduction}

glscopeclient, libscopehal, and the remainder of the project are all released under the 3-clause BSD license
(reproduced below). This is a permissive license, explicitly chosen to encourage integration with third-party open
source and commercial projects.

\section{License Agreement}

Copyright (c) 2012-2020 Andrew D. Zonenberg and contributors.
All rights reserved.

Redistribution and use in source and binary forms, with or without modification, are permitted provided that the
following conditions are met:
\begin{itemize}
\item Redistributions of source code must retain the above copyright notice, this list of conditions, and the
following disclaimer.
\item Redistributions in binary form must reproduce the above copyright notice, this list of conditions, and the
following disclaimer in the documentation and/or other materials provided with the distribution.
\item Neither the name of the author nor the names of any contributors may be used to endorse or promote products
derived from this software without specific prior written permission.
\end{itemize}

THIS SOFTWARE IS PROVIDED BY THE AUTHORS "AS IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED
TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL
THE AUTHORS BE HELD LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
(INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR
BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE
POSSIBILITY OF SUCH DAMAGE.

\section{Trademarks}

This document frequently mentions the names of various test equipment vendors and products in order to discuss
glscopeclient's compatibility with said products. The reader should assume that these are all trademarks of their
respective owners.

\section{Third Party Licenses}

TODO:
\begin{itemize}
\item yaml-cpp (shared, MIT license)
\item gtkmm (shared, LGPL)
\item FFTS (shared, BSD-3)
\item liblxi (shared, BSD-3/EPICS)
\end{itemize}

\subsection{avx\_mathfun.h (zlib license)}

AVX implementation of sin, cos, sincos, exp and log

Based on "sse\_mathfun.h", by Julien Pommier
http://gruntthepeon.free.fr/ssemath/

Copyright (C) 2012 Giovanni Garberoglio
Interdisciplinary Laboratory for Computational Science (LISC)
Fondazione Bruno Kessler and University of Trento
via Sommarive, 18
I-38123 Trento (Italy)

This software is provided 'as-is', without any express or implied
warranty.  In no event will the authors be held liable for any damages
arising from the use of this software.

Permission is granted to anyone to use this software for any purpose,
including commercial applications, and to alter it and redistribute it
freely, subject to the following restrictions:

\begin{enumerate}
\item The origin of this software must not be misrepresented; you must not
claim that you wrote the original software. If you use this software
in a product, an acknowledgment in the product documentation would be
appreciated but is not required.
\item Altered source versions must be plainly marked as such, and must not be
misrepresented as being the original software.
\item This notice may not be removed or altered from any source distribution.
\end{enumerate}
