\chapter{Export Formats}
\label{chap:exports}

\section{CSV}

Exports waveform data to a comma-separated-value file.

The first two columns of the generated file contain the X and Y values of the timebase reference channel (the channel
selected on the first page of the export wizard). Each sample in this channel maps directly to a row in the generated
CSV. Any waveform-type channel can be selected for export, however eye patterns, spectrograms, and other 2D density
plots cannot be used.

The second page of the wizard allows additional channels to be added to the export. Each channel maps to an additional
column in the generated CSV. The wizard will only allow channels with compatible X axis units; for example if the first
channe has X axis units of time then it will not be possible to add a channel with X axis units of frequency to the
same CSV.

Since the first channel serves as a timebase reference, all subsequent channels in the exported data share the same
timestamps as the first channel. If the channels are not sampled at identical times, the following resampling
algorithms are used for additional channels:

\begin{itemize}
\item Analog data: linear interpolation
\item Digital data: nearest neighbor
\item Protocol data: No interpolation. Protocol events are displayed as close as possible to their start timestamp;
remaining cells are blank.
\end{itemize}

\section{Touchstone}

Exports S-parameter data to a Touchstone 1.1 file with an arbitrary number of ports.

The exporter expects waveform data in mag/angle format. Magnitude channels must have X axis units of Hz and Y axis
units of dB; angle channels must have X axis units of Hz and Y axis units of degrees. While input data need not be
\emph{uniformly} sampled, all input channels must be sampled at the same set of frequencies.

Frequency units for the generated file can be selected as Hz, kHz, MHz, or GHz.

The export wizard allows mag/angle, dB mag/angle, or real/imaginary format to be selected. However, as of this writing
only mag/angle is actually implemented. Selecting any other format will result in a warning on the console; the file
will be generated in mag/angle format regardless of the user's choice.
